\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-08-15 paper.tex
Updated Figure 2
Removed testing Figure for axes

--\textgreater{}

@@

\begin{center}
\includegraphics[width=1\textwidth,height=\textheight]{paper_files/figure-pdf/unnamed-chunk-28-1.pdf}
\end{center}

@@

\begin{center}
\includegraphics[width=1\textwidth,height=\textheight]{paper_files/figure-pdf/unnamed-chunk-61-1.pdf}
\end{center}

>>>>

@@

@@

\begin{center}
\includegraphics[width=1\textwidth,height=\textheight]{paper_files/figure-pdf/unnamed-chunk-60-1.pdf}
\end{center}
